%frontmatter

\documentclass[../main/main.tex]{subfiles}

\begin{document}

%\section*{Copyright}
%\null\vfill
%\noindent
%\centering Copyright 2018 -- Lori D. Pickering\\
%\newpage
%\cleardoublepage

\section*{Disclaimer}
The views in this master thesis are that of the author's.  They do not in anyway represent the views of the United States Air Force Research Laboratory (AFRL)  or  the College of Engineering and Computer Science at Syracuse University. 
\cleardoublepage

\section*{Acknowledgements}
This research began in the summer of 2017 as part of the Assured by Design (ABD) program funded by the United States Air Force Research Laboratory (AFRL) in Rome, NY and managed by the principal investigator Professor Shiu-Kai Chin from the College of Engineering and Computer Science at Syracuse University.  This project was envisioned by Professor Shiu-Kai Chin to satisfy the needs of the ABD program.  This master thesis evolved directly from this work.

Thanks and recognition go to the following people for their contribution to this project.\\
Professor Shiu-kai Chin for providing me with the opportunity and for his faith in me and my capabilities on this project.  Erich Devendorf at AFRL for making the ABD program happen. Mizra Tihic for making this happen, especially with respect to funding.

A significant contributor to this research is U.S. Army Captain Jesse Nathaniel Hall who is also a graduate student at Syracuse University in the School of Information Science (iSchool).  The diagram in the front cover is his work.  His translation of the patrol base operations from the U.S. Ranger Handbook is a significant contribution and it is noted where appropriate in this master thesis.

Another contributor to this research is YiHong Guo, an undergraduate student at Syracuse University in the College of Engineering and Computer Science. YiHong's contribution includes the original documentation\footnote{YiHong's work does not appear in this master thesis.  However, he was very helpful and deserves some credit.} of this work in LaTeX.  

\end{document}
